The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-11-02 ApJ/ms.tex
Making changes in response to the first two points in the referee report.

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
stars enrich the surrounding intergalactic medium (IGM) when they go
supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.  The host
halo and the neighboring halos are then enriched with this ejecta.
There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
occur if the gas cooling is suppressed to the cosmic microwave
background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
  2009ApJ...691..441S}.  The resulting Population II star cluster will
thus have a lower characteristic stellar mass than its metal-free
progenitors.  These first stellar clusters may be connected to stars
in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
both with a metallicity floor of [Z/H]\footnote{We use the
  conventional notation, [Z/H] $\equiv$ log(Z/H) -
  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
  Tafelmeyer10}.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a,
  Yoshida08}.  They form in molecular clouds that coexist with the
dark matter halo center with limited fragmentation occurring during
their collapse; however \citet{2009Sci...325..601T} and
\citet{Stacy10_Binary} have shown that Pop III binaries may form in a
fraction of such halos.  There have been some recent hints that the
accretion disk around the first protostar may fragment and produce
clustered Pop III star formation \citep{Clark11_Frag,
  Greif11_P3Cluster}.  The final stellar masses in the aforementioned
calculations are still highly uncertain with a limited number of
samples.  Nevertheless, they all point toward an IMF with a larger
characteristic mass than present-day star formation.

>>>>

The first (Pop III) stars are metal-free and have a large
characteristic mass.  Previously, these stars were believed to be
massive, with universally suppressed fragmentation \citep{ABN02,
Bromm02_P3, OShea07a}.  Recently, several studies have suggested that
while fragmentation at times prior to the formation of the first
protostar may occur at scales of $1000-2000~\mathrm{AU}$, such
fragmentation is likely to result in high-mass, low-multiplicity
groups \citep{2009Sci...325..601T, Stacy10_Binary}.  Subsequent
studies have suggested that at later times, subsequent to the
formation of the first protostar, additional fragmentation may proceed
\citep{Greif11_P3Cluster, Clark11_Frag}.  A fraction of high-mass,
metal-free stars enrich the surrounding intergalactic medium (IGM)
when they go supernova, which can happen in stars $\lsim 40~\Ms$ in
Type II supernovae (SNe) or in stars roughly between 140 \Ms~and 260
\Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
The host halo and the neighboring halos are then enriched with this
ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
Z_\odot$ if dust cooling is efficient \citep{Omukai05,
Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
lowering its Jeans mass.  An intermediate characteristic mass of
$\sim10~\Ms$ can occur if the gas cooling is suppressed to the cosmic
microwave background (CMB) temperature \citep{Larson98,
Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
star cluster will thus have a lower characteristic stellar mass than
its metal-free progenitors.  These first stellar clusters may be
connected to stars in the Milky Way halo and nearby dwarf spheroidal
(dSph) galaxies, both with a metallicity floor of [Z/H]\footnote{We
use the conventional notation, [Z/H] $\equiv$ log(Z/H) -
log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
Tafelmeyer10}.

@@

Simulations following the full accretion history of Pop III stars,
from their formation inside cosmological minihalos through
transitioning onto the main sequence, are not currently possible.
However, under the assumption of spherical accretion, reasonable
estimates of the mass ranges for Pop III stars can be made by
extrapolating forward in time the instantaneous accretion rate at the
time of formation of the first protostellar core and comparing the
timescales for accretion against the Kelvin-Helmholtz time.  Several
studies, conducting this extrapolation, have shown that the
characteristic mass of Pop III stars $M_{\rm char} \sim 100~\Ms$
\citep{ABN02, Bromm02_P3, OShea07a, Yoshida08}.  They form in
molecular clouds that coexist with the dark matter halo center with
limited fragmentation occurring during their collapse; however
\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have shown that
Pop III binaries may form in a fraction of such halos.  There have
been some recent hints that the accretion disk around the first
protostar may fragment and produce clustered Pop III star formation
\citep{Clark11_Frag, Greif11_P3Cluster}.  The final stellar masses in
the aforementioned calculations are still highly uncertain with a
limited number of samples.  Nevertheless, they all point toward an IMF
with a larger characteristic mass than present-day star formation.
